Reproducing Analyses for Phenotypic evolution is less constrained in complex

### 2018-10-23 analyses/reproduce_analyses.Rmd
analyses updates

@@

@@

<!-- We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
Larva survival (0 or 1) was our response variable and measure of fitness. 
<!-- Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients. -->
<!-- We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape. 
This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.

@@

>>>>

```{r Bias in gradients on chamber diameter}
fixef(biased.diam_model_4)["sc.Diam"]
```

```{r Variance explained in chamber diameter}
chamber_diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), data=gall_selection.df)
summary(chamber_diam)
car::Anova(chamber_diam, test="F")

# variance explained by gall ID
0.5374/(0.5374+0.0956+0.1671+0.2031)
```

```{r Variance explained in other traits}
clutch_size <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, Gall_Number, sc.log.Clutch))
summary(clutch_size)
car::Anova(clutch_size, test="F")

female_pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, sc.log1p.Pref))
summary(female_pref)
car::Anova(female_pref, test="F")
```

```{r female pref plot, echo=F}
visreg::visreg(female_pref, xvar="Foodweb")
```

@@

```{r Levene tests}
platy_Diam_levene
platy_Clutch_levene
platy_Pref_levene
```

@@

<!-- We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
Larva survival (0 or 1) was our response variable and measure of fitness. 
<!-- Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients. -->
<!-- We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape. 
This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models. -->

@@

## Contributions of egg parasitoids to selection gradients

To identify the mechanisms by which food-web treatment altered selection gradients, we refit our models so that the complex food-web treatment only contained cases of parasitisms from egg parasitoids. Therefore, these analyses identify the change in apparent selection imposed by the egg parasitoid (egg parasitoid from simple food web; egg parasitoid from complex food web).

```{r Egg vs. egg Parasitoids Model, cache=TRUE}

# excludes cases of egg-parasitism from Complex food web
egg.vs.egg_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) #%>% 
 # mutate(Foodweb = ifelse(Foodweb == "Simple", "Egg", "egg"))

egg.vs.egg_df$Foodweb <- relevel(factor(egg.vs.egg_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids

egg.egg_model_1 <- update(model_1, data=egg.vs.egg_df)
summary(egg.egg_model_1)
```

```{r egg vs egg ggplot explore}
densities <- gall_selection.df %>%
  distinct(Foodweb, Genotype, Plant_Position, sc.log1p.Pref, Density_per_100_shoots)

survival <- gall_selection.df %>%
  group_by(Foodweb, Plant_Position) %>%
  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
  ungroup() %>%
  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)

left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  ggplot(., aes(x=sc.log1p.Pref, y=ectos_sum/ptoids_sum)) +
  geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial")) #+
  #scale_x_continuous(limits=c(-2,1.25))

left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  ggplot(., aes(x=sc.log1p.Pref, y=egg_parasitoid_sum/ptoids_sum)) +
  geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))

left_join(densities, survival) %>%
  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_sum/gall_survival_n, color=Foodweb)) +
  geom_point(aes(size=gall_survival_n), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))

left_join(densities, survival) %>%
  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_n, color=Foodweb)) +
  geom_point(aes(size=gall_survival_n), shape=21) +
  geom_smooth(method = "lm", formula = y ~ x, aes(weight=gall_survival_n))

left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  ggplot(., aes(x=sc.log1p.Pref)) +
  #geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) + 
  scale_x_continuous(limits=c(-1,1))

left_join(densities, survival) %>%
  filter(Foodweb=="Simple") %>%
  ggplot(., aes(x=sc.log1p.Pref)) +
  #geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +  # geom_smooth(method = "lm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green")
  scale_x_continuous(limits=c(-1,1))

# in the complex food web, there is a positive relationship between the number of gall samples and gall density (makes sense); there is the opposite pattern in the simple foodweb...
density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival))
visreg::visreg(density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
summary(density_n_lm)
wt_density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival), weights = gall_survival_n)
visreg::visreg(wt_density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
summary(wt_density_n_lm)

# good thing is that I get the same qualitative answer with or without weighting
test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial")
visreg::visreg(test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
summary(test_glm)

wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial", weights = gall_survival_n)
visreg::visreg(wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
summary(wt_test_glm)

# now with just egg parasitoids
egg.densities <- egg.vs.egg_df %>%
  distinct(Foodweb, Plant_Position, sc.log1p.Pref)

egg.survival <- egg.vs.egg_df %>%
  group_by(Foodweb, Plant_Position) %>%
  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
  ungroup() %>%
  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)

egg.test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial")
visreg::visreg(egg.test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
summary(egg.test_glm)

egg.wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial", weights = gall_survival_n)
visreg::visreg(egg.wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
summary(egg.wt_test_glm)

## now use raw densities
sqrt.raw_complex <- left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
  #geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
      geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
  #facet_wrap(~Genotype, ncol=2, nrow=4)

sqrt.raw_simple <- left_join(densities, survival) %>%
    filter(Foodweb=="Simple") %>%
    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
    ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
    #geom_point(aes(size=ptoids_sum), shape=21) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
   # facet_wrap(~Genotype, ncol=2, nrow=4)

plot_grid(sqrt.raw_complex, sqrt.raw_simple, ncol=2)

raw_complex <- left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
  ggplot(., aes(x=(Density_per_100_shoots))) +
  #geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
      geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
  #facet_wrap(~Genotype, ncol=2, nrow=4)

  raw_simple <- left_join(densities, survival) %>%
    filter(Foodweb=="Simple") %>%
    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
    ggplot(., aes(x=(Density_per_100_shoots))) +
    #geom_point(aes(size=ptoids_sum), shape=21) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
    geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
   # facet_wrap(~Genotype, ncol=2, nrow=4)

plot_grid(raw_complex, raw_simple, ncol=2)

log1p.raw_complex <- left_join(densities, survival) %>%
  filter(Foodweb=="Complex") %>%
  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
  ggplot(., aes(x=log1p(Density_per_100_shoots))) +
  #geom_point(aes(size=ptoids_sum), shape=21) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
  scale_y_continuous(limits=c(0,1)) + #scale_x_continuous(limits=c(0,100)) +
      geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
  #facet_wrap(~Genotype, ncol=2, nrow=4)

log1p.raw_simple <- left_join(densities, survival) %>%
    filter(Foodweb=="Simple") %>%
    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
    ggplot(., aes(x=log1p(Density_per_100_shoots))) +
    #geom_point(aes(size=ptoids_sum), shape=21) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
    scale_y_continuous(limits=c(0,1)) +# scale_x_continuous(limits=c(0,100)) +
    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
   # facet_wrap(~Genotype, ncol=2, nrow=4)

plot_grid(log1p.raw_complex, log1p.raw_simple, ncol=2)

left_join(densities, survival) %>%
  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
    #geom_point(aes(size=ptoids_sum), shape=21) +
    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n, color=Foodweb), method.args = list(family="binomial")) +
  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted")

ggplot(densities, aes(x=Genotype, y=Density_per_100_shoots, fill=Foodweb)) + geom_boxplot()
ggplot(densities, aes(x=Genotype, y=sc.log1p.Pref, fill=Foodweb)) + geom_boxplot()

summary(lm(Density_per_100_shoots ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
summary(lm(sqrt(Density_per_100_shoots) ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
car::Anova(lmer(sqrt(Density_per_100_shoots) ~ Foodweb + (1|Genotype), filter(densities, Density_per_100_shoots>0)), test="F")
summary(lm(sc.log1p.Pref ~ Foodweb, densities))

with(densities, table(Foodweb, Density_per_100_shoots))

ggplot(densities, aes(x=Density_per_100_shoots, fill=Foodweb)) + geom_density(alpha=0.5)
ggplot(densities, aes(x=sqrt(Density_per_100_shoots), fill=Foodweb)) + geom_density(alpha=0.5)
ggplot(densities, aes(x=sc.log1p.Pref, fill=Foodweb)) + geom_density(alpha=0.5)

shapiro.test(densities$Density_per_100_shoots)
shapiro.test(sqrt(densities$Density_per_100_shoots))
shapiro.test(log1p(densities$Density_per_100_shoots))

clutches <- gall_selection.df %>%
  distinct(Foodweb, Genotype, Plant_Position, sc.log.Clutch, gall_individuals)
shapiro.test((clutches$gall_individuals))
shapiro.test(sqrt(clutches$gall_individuals))
shapiro.test(log(clutches$gall_individuals))

shapiro.test((gall_selection.df$Gall_Height_mm))
shapiro.test(sqrt(gall_selection.df$Gall_Height_mm))
shapiro.test(log(gall_selection.df$Gall_Height_mm))
```

```{r Egg vs. Egg Bootstrap Model 1, include=FALSE, cache=TRUE}
egg.egg_boot_model_1 <- bootMer(egg.egg_model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

egg.egg_tidy_model_1 <- tidy(egg.egg_boot_model_1, conf.int=T) %>% 
  # filter terms that only matter for this analysis
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)",
                     "FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"))
```

There is no strong evidence that egg parasitism differs for nonlinear terms between complex and simple food webs. Although close perhaps for sc.Diam.

```{r Egg vs. Egg Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE}
knitr::kable(egg.egg_tidy_model_1)

egg.egg_plot_model_1 <- egg.egg_tidy_model_1 %>%
  mutate(Food_web = ifelse(grepl("FoodwebComplex", .$term)==TRUE,"Complex","Simple")) %>%
  filter(Food_web == "Complex")

egg.egg_plot_model_1$term_plot <- factor(egg.egg_plot_model_1$term,
                                levels=c("FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"),
                                ordered=TRUE)

egg.egg_plot_model_1 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_1$term_plot))) +
  ylab("Coefficient (logit scale)")

visreg::visreg(egg.egg_model_1, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
```

```{r Fit Egg vs. egg Parasitoid Model 3, cache=TRUE}
egg.egg_model_3 <- update(model_3, data=egg.vs.egg_df) 
```

```{r Bootstrap Egg vs. egg Parasitoid Model 4, cache=TRUE, include=FALSE}
boot_egg.egg_model_3 <- bootMer(egg.egg_model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

tidy_egg.egg_model_3 <- tidy(boot_egg.egg_model_3, conf.int=T) 
```

Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
```{r Plot Egg vs. egg Parasitoid Model 4, echo=FALSE}
egg.egg_plot_model_3 <- tidy_egg.egg_model_3 %>%
  mutate(Food_web = ifelse(grepl("FoodwebComplex:", .$term)==TRUE,"Complex","Simple")) %>%
  filter(Food_web == "Complex")

egg.egg_plot_model_3$term_plot <- factor(egg.egg_plot_model_3$term,
                                levels=c("FoodwebComplex:sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebComplex:sc.log1p.Pref"),
                                ordered=TRUE)

egg.egg_plot_model_3 %>%
  ggplot(., aes(x=term_plot)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_3$term_plot))) +
  ylab("Coefficient (logit scale)")
```

```{r Fit Egg vs. egg Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE}
egg.egg_model_4_adj <- update(model_4_adj, data=egg.vs.egg_df)
```

This reduced model returns the same qualitative result as before. Specifically, that the linear effect of clutch size depends on food-web treatment. Note also that egg survival is significantly higher in the simple food web compared to the complex food web (dotted line). These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).

```{r Bootstrap Egg vs. egg Parasitoid adjuted Model 4, cache=TRUE, include=FALSE, eval=FALSE}
boot_egg.egg_model_4_adj <- bootMer(egg.egg_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)

tidy_egg.egg_model_4_adj <- tidy(boot_egg.egg_model_4_adj, conf.int=T) 
```

Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
```{r Plot Egg vs. egg Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE}
tidy_egg.egg_model_4_adj$term_ord <- factor(tidy_egg.egg_model_4_adj$term, 
                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
                                ordered = TRUE)

plot_egg.egg_model_4_adj <- tidy_egg.egg_model_4_adj %>%
  filter(term != "(Intercept)") %>%
  droplevels()

plot_egg.egg_model_4_adj %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(plot_egg.egg_model_4_adj$term_ord))) +
  ylab("Coefficient (logit scale)")
```

## CALCULATE SELECTION GRADIENTS FOR EGG VS. egg PARASITOIDS

```{r Organize and Transform egg vs. egg parasitoid Coefficients, include=FALSE, eval=FALSE}
tidy_egg.egg_coefs <- bind_rows(
  select(tidy_egg.egg_model_2_adj, term, estimate, conf.low, conf.high), 
  select(tidy_egg.egg_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
  filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects

# Tidy common coefficients
tidy_egg.egg_common_coefs <- tidy_egg.egg_coefs %>%
  filter(term!="FoodwebEgg:I(sc.log1p.Pref^2)", term!="Foodwebegg:I(sc.log1p.Pref^2)",
         term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")

# Tidy unique coefficients to each food-web
egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:I(sc.log1p.Pref^2)")
egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:I(sc.log1p.Pref^2)")
egg_quad_pref$term <- "I(sc.log1p.Pref^2)"

egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:sc.log.Clutch")
egg_clutch$term <- "sc.log.Clutch"
egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:sc.log.Clutch")
egg_clutch$term <- "sc.log.Clutch"
```

```{r Calculate Egg vs. egg parasitoid Selection Gradients, include=FALSE, eval=FALSE}

# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="egg"), type="response")
egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
egg_mean_fitness <- mean(egg_predict)

egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="Egg"), type="response")
egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
egg_mean_fitness <- mean(egg_predict)

# Double-check that using a different model (e.g. egg.egg_model_4) doesn't influence estimes of mean "brackets" and mean fitness. Using "Complex" food-web treatment as an example, but it doesn't matter 
alt_egg.egg_predict <- predict(egg.egg_model_4, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
alt_egg.larval_mean_brackets <- mean(alt_egg.larval_predict * (1 - alt_egg.larval_predict))
alt_egg.larval_mean_fitness <- mean(alt_egg.larval_predict)
test_egg.larval_mean_brackets <- larval_mean_brackets
test_egg.larval_mean_fitness <- larval_mean_fitness
test_egg.larval_mean_brackets - alt_egg.larval_mean_brackets # virtually the same
test_egg.larval_mean_fitness - alt_egg.larval_mean_fitness # virtually the same

```{r Table of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
                                   ordered = TRUE)

```{r Plot of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
egg.larval_selection_gradients %>%
  ggplot(., aes(x=term_ord)) +
  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted") +
  scale_x_discrete(name="", limits = rev(levels(egg.larval_selection_gradients$term_ord))) +
  ylab("Selection Gradient") +
  scale_fill_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) +
  scale_color_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) 
```
